Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2018-06-09 paper/referee_reply1.txt

1) The size-halo connection that the authors advocate, presented in Section 3.2.2, sets each galaxy to be 1% of the size of its halo at the time of Mpeak. The authors state below Eq 3 that this defines a _median_ relation between Reff and Mhalo, around which they assume a log-normal scatter of 0.2 dex. However, it seems that a more direct application of Eq 2 would be to apply it on a halo-by-halo basis, since Rpeak is known for every object in the catalogue. This would specify the full Reff distribution, with scatter deriving from the scatter in Rpeak. Why is this not done? No justification is given for using a log-normal scatter of 0.2 dex.

Reply) The concluding sentence to Section 3.2.2 was indeed confusing; it turns out it was also misleading: in fact, in our analysis we assigned R_1/2 in exactly the fashion the referee described, about each halo's own R_Mpeak. We have changed the language to more accurately reflect the implementation of the model, and thank the referee for pointing out this confusing language.

2) This model is compared to one in which Reff does not correlate with any halo property at fixed stellar mass, but simply depends on M* in a manner that reproduces the M*-Reff relation by construction. Again the authors take 0.2 dex scatter around the median relation, but if one really wanted to reproduce the M*-Reff relation -- including its scatter -- one would take this scatter in bins of M* from the data. Even better would be to drop the assumption of Gaussian scatter altogether and simply assign a size randomly to each model galaxy by sampling the observed Reff distribution at given M*. It appears the authors' choice is motivated by a desire for compatibility with Somerville et al 2017, but it is unclear why this is especially relevant or important here.

We agree with the referee that drawing directly from P_SDSS(R_1/2 | M*) would improve the fidelity of our model with respect to the SDSS. However, our goal here is actually twofold. On the one hand, we want to identify a model that has sufficient flexibility to capture size-dependent clustering with good accuracy, using SDSS as our validation dataset. On the other hand, we are attempting to build a class of models that can be applied equally well to other datasets, including those may not have the statistics of the SDSS, as is the case in present-day high-redshift surveys. We have added what we hope is a clarifying paragraph on this point towards the end of Section 7, repeated below for convenience:

---
We have attempted to anticipate such a joint analysis in our choices for the formulation of the model presented here. For example, for purposes of the scope of the present work alone, one could more accurately capture the complexity of the true distribution of $\rhalf$ by drawing directly from a numerical tabulation of $P_{\rm SDSS}(\rhalf\vert\mstar).$ Here we choose to approximate this distribution with a log-normal so that the same smooth, analytic model can be applied to datasets sparser than SDSS, e.g., pencil-beam high-redshift surveys. While we have kept the level of scatter in our log-normal distribution fixed to the value found in \cite{somerville_etal17}, our model formulation enables self-calibration of the true (possibly mass-dependent) stochasticity in future Bayesian inference analyses.
---

### 2018-06-09 paper/galsize_paper.tex
Replied to second comment and implemented revision

>>>>

We have attempted to anticipate such a joint analysis in our choices for the formulation of the model presented here. For example, for purposes of the scope of the present work alone, one could more accurately capture the complexity of the true distribution of $\rhalf$ by drawing directly from a numerical tabulation of $P_{\rm SDSS}(\rhalf\vert\mstar).$ Here we choose to approximate this distribution with a log-normal so that the same smooth, analytic model can be applied to datasets sparser than SDSS, e.g., pencil-beam high-redshift surveys. While we have kept the level of scatter in our log-normal distribution fixed to the value found in \cite{somerville_etal17}, our model formulation enables self-calibration of the true (possibly mass-dependent) stochasticity in future Bayesian inference analyses.
